\documentclass[11pt]{book}

\RequirePackage{silence}
\WarningFilter{remreset}{The remreset package}

\title{MAT246 - Concepts in Abstract Mathematics}
\author{Callum Cassidy-Nolan}

\input{mynotes-preamble.tex}

\begin{document}

\input{mynotes-header.tex}

\chapter{Lecture 1}%
\label{chp:lecture_1}
% chapter lecture_1

\section{Induction}%
\label{sec:induction}
% section induction

\begin{note}
    \[
    \mathbb{N} = \left\{ 1, 2, 3, \ldots  \right\} 
    \]
\end{note}

\begin{defn}[The principle of mathmatical induction ]\index{The principle of mathmatical induction }\label{defn:the_principle_of_mathmatical_induction_}
suppose $S \subseteq \mathbb{N} $  

If
\begin{itemize}
    \item $1\in S$ 
    \item $k + 1 \in S$ whenever $k \in S$ 
\end{itemize}
Then
\[
    \boxed{ S = \mathbb{N} }
\]

\end{defn}

The principle of mathmatical induction is simply saying if $1$ is in $S$ then $2, 3, \ldots $ is also in S

\begin{eg}
    Prove 
    \[
        \forall n \in \mathbb{N} , \underbracket{1^2  + 2^2  + \ldots  + n^2 = \frac{n\left( n + 1 \right) \left( 2n + 1 \right) }{6}}_{\chi} 
    \]
    \begin{proof}
    $ $\newline
        Let $S= \left\{ n \in \mathbb{N} : \chi \text{ holds }  \right\} $ At this point we don't know what $S$ consists of but we must show it is $\mathbb{N} $, then we can conclude that the formula holds for all natural numbers. We commence by verifying that $1\in S$, we have 
        \[
            1^2 = \frac{1\left( 1 + 1 \right) \left( 2 + 1 \right) }{6}
        \]
        both the right hand side and left hand side are equal to eachother, so the formula holds for $1$. 

        We will now show if $k \in S$ then $k + 1 \in S$. We assume that $k \in S$, that is :
        \[
            1^2  + 2^2  + \ldots  + k^2 = \frac{k\left( k + 1 \right) \left( 2k + 1 \right) }{6}
        \]
        We observe that if we add $k + 1$ to both sides of the above equation we get the left hand side, of what we want to prove.
        \begin{align*}
            1^2  + 2^2  + \ldots  + k^2  + \left( k + 1 \right) ^2 &= \frac{k\left( k + 1 \right) \left( 2k + 1 \right) }{6} + \left( k + 1 \right) ^2 \\
            &= \frac{k\left( k + 1 \right) \left( 2k + 1 \right)  + 6\left( k + 1 \right) ^2 }{6}  \\ 
            &= \frac{\left( k + 1 \right) \left( k\left( 2k + 1 \right)  + 6\left( k + 1 \right)  \right) }{6}  \\ 
            &= \frac{\left( k + 1 \right) \left( 2k^2  + 7k + 6 \right) }{6}  \\ 
            &= \frac{\left( k + 1 \right) \left( k + 2 \right) \left( 2k + 3 \right) }{6} \\ 
            &= \frac{\left( k + 1 \right) \left( \left( k + 1 \right)  + 1  \right) \left( 2\left( k + 1 \right)  + 1 \right) }{6}  \\ 
        \end{align*}
        After working out the right hand side it is the original formula with $k + 1$ subbed in. Therefore we have shown that  if $k \in S$ then $k + 1 \in S$ as wanted, thus by the principle of mathmatical induction 
        \[
        S= \mathbb{N} 
        \]
        .
    \end{proof}
\end{eg}

\newpage

\begin{defn}[Extended principle of mathmatical induction ]\index{Extended principle of mathmatical induction }\label{defn:extended_principle_of_mathmatical_induction_}
    This is the same as normal induction, though now we don't have to start with 1.
    If  
    \begin{itemize}
        \item Let $n_{0} \in \mathbb{N} , n_{0} \in S$
        \item $k \in S \implies k + 1 \in S$ 
    \end{itemize}
    Then
    \[
    \boxed{S \supseteq \left\{ n_{0} , n_{0}  + 1, \ldots  \right\}  }
    \]
    Observe that $S$ is only a subset of these numbers as these are the ones that are guarenteed to be in $S$, there may be others. 
\end{defn}

\begin{eg}
    Prove for all integers $n$ greater than or equal to 7 that the following holds:
    \[
        \underbracket{ n! \ge 3^{n} }{\chi}
    \]
    \begin{proof}
    $ $\newline
        Let $S$ be the set of all natural numbers that $\chi $ holds for. We verify that $7 \in S$ 
        \[
        \underbracket{7!}_{5040} \ge \underbracket{3^{7} }_{2187} 
        \]
        therefore 7 satisfies $\chi$ and so $7 \in S$.
        Let $k \in \mathbb{N} $,  we assume $\chi$ holds for $k$, that is 
        \[
        k! \ge 3^{k} 
        \]
        We will prove 
        \[
            \left( k + 1 \right) ! \ge 3^{k + 1} 
        \]
        We observe that $\left( k + 1 \right) ! = \left( k + 1 \right) k!$, but recall that we assumed that $k! \ge 3^{k} $ so we have 
        \begin{align*}
            k!\left( k + 1 \right) &\ge 3^{k} \left( k + 1 \right) \\
            \intertext{Recall that $k\ge 7$ }
            &\ge 3^{k} 8   \\ 
            &\ge 3^{k + 1}
        \end{align*}
        Therefore, we've shown that
        \[
            \left( k + 1 \right) ! \ge 3^{k + 1} 
        \]
        as required, and so 
        \[
        S \supseteq \left\{ 7, 8, 9, \ldots  \right\} 
        \]
    \end{proof}
    
\end{eg}

% section induction (end)

\chapter{Section One Problems}%
\label{chp:section_one_problems}
% chapter section_one_problems

\paragraph{composite} 
\begin{itemize}
    \item $2\mid 68$ 
    \item $3\mid 129$
    \item $2\mid 20,101,116$  
\end{itemize}

\paragraph{primes} 
\begin{itemize}
    \item Maybe?
    \item no, $3 \mid 153$ 
    \item Maybe?
    \item no, $2 \mid 851, 486$ 
\end{itemize}

\paragraph{sum of primes} 
\begin{itemize}
    \item $97 + 3= 100$ ?
\end{itemize}

% chapter section_one_problems (end)

% chapter lecture_1 (end)

\chapter{Lecture 2}%
\label{chp:lecture_2}
% chapter lecture_2

\begin{defn}[Well Ordering Principle]\index{Well Ordering Principle}\label{defn:well_ordering_principle}
   Every subset of $\mathbb{N} $ other than $\emptyset $ has a smallest      element. 
\end{defn}

\section{Proof of Induction}%
\label{sec:proof_of_induction}
% section proof_of_induction

\begin{remark}
    We accepted the Principle of Mathematical Induction, though we should prove it.
\end{remark}

Recall, the Principle of Mathematical Induction, suppose $S \subseteq N$, if  
\begin{itemize}
    \item $1 \in S$ 
    \item $k + 1 \in S$ whnever $k\in S$ 
\end{itemize}
then 
\[
S= \mathbb{N} 
\]

We'll prove the statement
\begin{proof}
$ $\newline
    Let $T= \left\{ n\in \mathbb{N} : n \not\in S  \right\} $. suppose that $T\neq \emptyset $,  therefore by the Well Ordering Principle we know that $T$ has a smallest element, let $n_{0} $ be that element. Note that $n_{0} \in \mathbb{N}, n_{0} \neq 1 $ since $1\in S \therefore 1 \not\in T$, therefore $n_{0} \ge 2$.\\
    since $n_{0} \ge 2 $ we know $n_{0}  - 1 \in \mathbb{N} $ and that $n_{0}  - 1 \not\in T$ since $n_{0} $ is the smallest element in $T$. 
    \[
    n_{0}  - 1 \not\in T \implies n_{0}  - 1 \in S
    \]
    But by property 2, of $S$ we know that if $n_{0} \in S$ then $n_{0} \in S$,  though this is a contradiction as $n_{0} \not\in S$\\
    Therefore $T = \emptyset $ and $S = \mathbb{N} $ 
\end{proof}


% section proof_of_induction (end)

\section{Division}%
\label{sec:division}
% section division

\begin{defn}[Divides]\index{Divides}\label{defn:divides}
    for $a, b \in \mathbb{N} $ we say that $a$ divides $b$ if there exists a $c \in \mathbb{N} $ such that 
    \[
    b= ca
    \]
    And we say 
    \[
    a \mid b
    \]
\end{defn}
\begin{remark}
    $2 \cdot 3.5 = 7$, though our definition is only for natural numbers, since no $c \in \mathbb{N} $ gives $2 \cdot c = 7$ 
\end{remark}

\begin{defn}[Prime]\index{Prime}\label{defn:prime}
    $p \in \mathbb{N} $ is \underline{prime} if the only divisor of $p$ are $1 \text{ and } p$ and $p\neq 1$ 
\end{defn}

\paragraph{Example} 
\begin{itemize}
    \item 7 is prime, since the only divisor is 1 and 7
    \item 10 is not prime, 2 and 5 divide 10
\end{itemize}

\begin{thm}[Product of Primes]\index{Product of Primes}\label{thm:product_of_primes}
    for all $n \in \mathbb{N} ,n \neq 1$ $n$ can be written as a product of primes 
\end{thm}

\paragraph{Example} 
\begin{itemize}
    \item $42 = 2  \cdot 3 \cdot 7$ 
    \item $12 = 3  \cdot 2^{2} $ 
\end{itemize}

\newpage

\begin{defn}[Complete Induction]\index{Complete Induction}\label{defn:complete_induction}
    Let $S\subseteq \mathbb{N} $ 
    \begin{itemize}
        \item if $n_{0} \in S$ 
        \begin{itemize}
            \item and $k + 1 \in S$ when $n_{0} , n_{0}  + 1, \ldots , k \in S$ 
        \end{itemize}
        Then 
        \[
        S \supseteq \left\{ n_{0} , n_{0}  + 1, \ldots  \right\} 
        \]
    \end{itemize}
\end{defn}

We will prove the product of primes theorem
\begin{proof}
$ $\newline
    Let $S= \left\{ n \in \mathbb{N} : \text{ theorem holds for } n \right\} $ we will prove 
    \[
    S= \mathbb{N} 
    \]
    \begin{itemize}
        \item 2, is prime therefore it is a product of primes and so the Base Case holds. 
        \item We assume if $2, 3, \ldots , k \in S$ then $k + 1 \in S$ 
            \begin{itemize}
                \item \textbf{Case 1}: $k + 1$ is prime, then we are done like the base case
                \item \textbf{Case 2}: $k + 1$  is not prime, then there exists an $m \in \mathbb{N} $ such that $1 < m < k + 1$ and $m \mid k + 1$ by definition this means 
                    \[
                    k + 1 = c \cdot m, \text{ for some } c \in \mathbb{N} 
                    \]
                    observe that $1 < c < k + 1$ since if $c = 1$,$c= k + 1$ or if larger we get a contradiction.\\
                    Therefore we can use the Induction Hypothesis on $c \text{ and } m$ to write thpem both as a product of primes, multiplying them together gives us a new product of primes equal  to $k + 1$ as required. 
            \end{itemize}
    \end{itemize}
Therefore by the principle of complete induction we can say that 
\[
S \supseteq \left\{ 2, 3, \ldots  \right\} 
\]
though we want to show that $S= \left\{ 1, 2,3, \ldots  \right\} $ observe  that $1$ is not a product of primes as it is not prime and also not composite, therefore $1 \not\in S$ so $S= \left\{ 2, 3, \ldots  \right\} $  
\end{proof}

The intuition behind this proof comes from the fact that if we take a number say $24$ it is either prime  or not, in this case it is not, and we can write it as $24 = 6  \cdot 4$ then by an inductive argument, we already know that $6 $  and $4$ are already product of primes so we are done. We will show next that in fact this is a unique product.

% section division (end)

% chapter lecture_2 (end)

\chapter{Lecture 3}%
\label{chp:lecture_3}
% chapter lecture_3

Recall from last lecture we showed that every natural number besides 1 can be written as a product of primes. Thus we have the following 
\[
\forall n \in \mathbb{N} , n \ge 1 \implies n \text{ is divisible by some prime } 
\]
Let's call the above $\alpha $ 


\section{There is no largest prime}%
\label{sec:there_is_no_largest_prime}
% section there_is_no_largest_prim

\begin{proof}
$ $\newline
    suppose by contradiction $p$ is the largest prime, that is 
    \[
    \left\{ 2, 3, \ldots , p \right\} 
    \]
    are all the primes.
    Let $m= \left( 2 \cdot 3 \cdot \dotsm  \cdot p \right)  + 1$,  we note that for any $j \in \left\{ 2, 3, \ldots ,p \right\} $ they must not division $m$ as they each of a remainder of 1. We observe that $m \ge 1$ thus by $\alpha $ we know that there exists some $q \in \mathbb{N} $ where $q$ is prime such that 
    \[
    q \mid m
    \]
    So then $q \neq 2, 3, \ldots ,p$ and so we have found a new prime, which contradicted that we had found all primes, so we get a contradiction, therefore there is no largest prime.
\end{proof}

% section there_is_no_largest_prime (end)

% chapter lecture_3 (end)

\chapter{Lecture 4}%
\label{chp:lecture_4}
% chapter lecture_4

\begin{thm}[Fundamental Theorem of Arithmetic]\index{Fundamental Theorem of Arithmetic}\label{thm:fundamental_theorem_of_arithmetic}
    Every natural number other than 1, is a product of primes (proved last lecture) and the primes in the product are unique (including multiplicity)  except for the order in which they occur.
\end{thm}

Recall given $n\in \mathbb{N}, n \neq 1, n $ is a product of primes that is 
\[
n = p_1 p_2 \dotsb p_{k - 1} p_{k}
\]

for example 
\[
180 = 9 \cdot 10 \cdot 2= 3^{2} 5^{1} 2^{2} 
\]

So equivalently we have 
\[
\forall n \in \mathbb{N} , 1 < n \implies n = p_{1} ^{\alpha _{1} } p_{2} ^{\alpha _{2} } \dotsm p_{k} ^{\alpha _{k} }  
\]
where $p_{i} $ are distinct primes and $\alpha _{i} \in \mathbb{N} $ 

We will prove that the prime factorization of any natural number greater than 1 has is unique by contradiction.

\newpage

\begin{proof}
$ $\newline
We commence
\begin{itemize}
    \item Suppose there are some numbers with two distinct factorizations into primes.
    \item Let $\mathcal{X} $ be the set of these numbers, observe that $\mathcal{X} \subseteq \mathbb{N} $ thus by the Well Ordering Principle we let $n$ be the smallest such number in $\mathcal{X} $, we have 
        \[
        n= p_1 p_2 \dotsb p_{k - 1} p_{k} = q_1 q_2 \dotsb q_{l - 1} q_{l}
        \]
        (Note here we aren't using powers, but we allow for repeated primes, and that $p_{i} ,q_{j} $ are primes)
    \item Suppose that the two product of primes share at least one factor, say $p_{r} = q_{r} $, then in each product of primes they cancel out and we get that a new smaller number that can be written as a product of primes, though this would cause a contradiction since we assumed $n$ was the smallest such number with this property. 
        \begin{itemize}
            \item Therefore all the $p_{i} $ are different than the $q_{j} $ 
        \end{itemize}
    \item Since we know $p_{i} \neq q_{j} $ then specifically $p_{1} \neq q_{1} $ if this is true there are two cases either $p_{1} \le q_{1} $ or $p_{1} \ge q_{1} $.
    \item \textbf{Case 1}: $p_{1} < q_{1} $ 
        \begin{itemize}
            \item We note $n = q_1 q_2 \dotsb q_{l - 1} q_{l} > p_1 q_2 \dotsb q_{l - 1} q_{l}$ 
            \item $p_1 q_2 \dotsb q_{l - 1} q_{l} < n \Leftrightarrow 0 < n - p_1 q_2 \dotsb q_{l - 1} q_{l}$ 
            \item Note that $p_{i} , q_{j} \in \mathbb{N} $ so the product of any of them is also an element of the naturals, and then also $n - p_1 q_2 \dotsb q_{l - 1} q_{l} \in \mathbb{N}$.
        \end{itemize}
    \item Note that $m < n \implies m$ has a unique factorization into primes \todo{Why?}, we know
        \begin{itemize}
            \item $m = p_1 p_2 \dotsb p_{k - 1} q_{k}  - q_1 q_2 \dotsb q_{l - 1} q_{l}= p_{1} \left( p_2 \dotsb p_{k - 1} p_{k} - q_2 \dotsb q_{l - 1} q_{l} \right) $ 
            \item $m = q_1 q_2 \dotsb q_{l - 1} q_{l} - p_1 q_2 \dotsb q_{l - 1} p_{l} = \left(  q_2 \dotsb q_{l - 1} q_{l} \right) \left( q_{1}  - p_{1}  \right) $ 
            \begin{itemize}
                \item Together
                    \[
 p_{1} \left( p_2 \dotsb p_{k - 1} p_{k} - q_2 \dotsb q_{l - 1} q_{l} \right) = \underbracket{\left(  q_2 \dotsb q_{l - 1} q_{l} \right)}_{\chi}  \left( q_{1}  - p_{1}  \right) 
                    \]
            \end{itemize}
        \end{itemize}
    \item The left hand side of the above tells us that $p_{1} $ is a prime factor of $m$ which means it is also a factor of the right hand side.
        \begin{itemize}
            \item But observe $p_{1} \nmid \chi$ since $p_{1} \neq q_{j} $ 
            \item Therefore it must be that $p_{1} | \left( q_{1}  - p_{1}  \right) $ this is true if and only if $p_{1} \mid q_{1} $ since $q_{1} $ is prime this means that $p_{1} = 1$ or $p_{1} = q_{1} $ either of which are contradictions, therefore this contradcicts our original assumption and so in fact every prime factorization is unique.
        \end{itemize}
\end{itemize}
\end{proof}

\paragraph{Techniques Used in this proof} 
\begin{itemize}
    \item Here
\end{itemize}

\begin{defn}[Composite]\index{Composite}\label{defn:composite}
    A natural number $c$ is called composite if
    \begin{align*}
        c \neq 1 && c \text{ is not prime } 
    \end{align*}
\end{defn}

Q: Can we find 20 consecutive composite numbers?

Yes, consider 
\[
21! + 2, 21!  + 3, \ldots , 21!  + 21
\]
Observe 2 divides the first number, 3, divides the next on until 21, giving us 20 composites

Q: Can we find $k$ consecutive composite numbers?

Yes, using hte same method we have 
\[
    \left( k + 1 \right)!  + 2, \left( k + 1 \right) !  + 3, \ldots , \left( k + 1 \right) !  + k + 1
\]
thus we conclude there are arbitrary long stretches of composite numbers.

\newpage

\section{Modular Arithmetic}%
\label{sec:modular_arithmetic}
% section modular_arithmetic

For some intuition, consider military time, if somone tells us it's 15 o clock we know that this is equivalent to 3 o clock, and this will help us represent this type of situation

First we define the integers that is 
\[
\mathbb{Z} = \left\{ 0, \pm 1, \pm 2, \ldots  \right\} 
\]

\begin{defn}[Congruence]\index{Congruence}\label{defn:congruence}
    Let $a, b \in \mathbb{Z} $,  $m \in \mathbb{N} $.  if 
    \[
        m \mid \left( a - b \right) 
    \]
    then we say $a$ is \underline{congruent} to $b$ and we write
    \[
    a \equiv b \Mod{m}
    \]
\end{defn}

\paragraph{Example} 
\begin{itemize}
    \item Let $m = 12$ (the hours on the clock)
        \begin{itemize}
            \item it follows that $13 \equiv 1 \Mod{12} $ since $12 \mid \left( 13  - 1 \right) $ 
            \item $14 \equiv 2 \Mod{12} $ and $23 \equiv -1 \Mod{12} $ 
            \item So this shows us in the world of the clock some numbers are the ``same"
        \end{itemize}
    \item $m = 2$ 
        \begin{itemize}
            \item We observe 
                \begin{itemize}
                    \item $0 \equiv 0 \Mod{2} \Leftrightarrow 2 \mid \left( 0  - 0 \right) $ which is true since we take $c = 0$ in the definition of divisibility.
                    \item $1 \equiv 1 \Mod{2} $ 
                    \item $2 \equiv 0 \Mod{2} $ 
                    \item $3 \equiv 1 \Mod{2} $ 
                    \item $4 \equiv 0 \Mod{2} $ 
                    \item $5 \equiv 1 \Mod{2} $ 
                \end{itemize}
        \end{itemize}
\end{itemize}

% section modular_arithmetic (end)

% chapter lecture_4 (end)

\chapter{Lecture 5}%
\label{chp:lecture_5}
% chapter lecture_5

\begin{remark}
    From last lecture we noted that $a \equiv b \Mod{m} $ which meant $m 
    \mid \left( a - b \right) $ that is $\left( a - b \right) = jm$ for some $j\in \mathbb{Z} $ then also $\left( b - a \right) =  - jm$ and so $m \mid \left( b - a \right) $ \todo{But our definition of div is for naturals?}  so 
    \[
    a \equiv b \Mod{m} \Leftrightarrow b \equiv a \Mod{m} 
    \]
\end{remark}

Suppose $k, m \in \mathbb{N} $ and 
\[
k = qm  + r, \text{ for some } q \in \mathbb{N} \text{ and } 0 \le r < m
\]
that is to say, $m$ goes in $q$ times with a remainder of $r$ into $k$ 

\begin{crly}
    A number is always congruent to it's remainder upon division by the modulus, amoung other numbers.
\end{crly}

\newpage

\section{Manipulating Congruences}%
\label{sec:manipulating_congruences}
% section manipulating_congruences

We will show that congruences are additive that is if $a \equiv b \Mod{m} \text{ and } c \equiv d \Mod{m} $ then $a + c \equiv b + d \Mod{m} $ 
\begin{proof}
    $ $\newline
    By definition 
    \begin{gather*}
        m \mid a - b \Leftrightarrow mk = a - b, \text{ for some } k \in \mathbb{Z} \\
        m \mid c  - d \Leftrightarrow ml = c  - d, \text{ for some } l \in \mathbb{Z} 
    \end{gather*}
    then taking the sum we have 
    \[
        m\left( k + l \right) = \left( a - b \right)  + \left( c  - d \right) = \left( a + c \right)  - \left( b + d \right) 
    \]
    and so $\left( a + c \right)  \equiv \left( b + d \right)  \Mod{m} $ 
\end{proof}

We will show that congruences are also multiplicative, that is to say if $a \equiv b \Mod{m} $ and $c \equiv d \Mod{m} $ then 
\[
a \cdot c \equiv b \cdot d \Mod{m} 
\]
\begin{proof}
$ $\newline
    By the same reasoning as the previous proof, we have 
    \begin{align*}
        mk = a - b && ml = c  - d
    \end{align*}
    need to show $m \mid ac  - bd$ 
    \begin{align*}
        ac - bd &= ac  - bc  + bc  - bd  \\ 
        &= c\left( a - c \right)  + b\left( c - d \right)   \\ 
        &= c\left( mk \right)  + b\left( ml\right)   \\ 
        &= m\left( ck  + bl \right)   \\ 
    \end{align*}
    and so $m \mid ac  - bd \Leftrightarrow a \cdot c \equiv b \cdot d \Mod{m} $ as required. 
\end{proof}

\paragraph{Quick Consequences} 
\begin{itemize}
    \item if $a \equiv b \Mod{m} $ then taking the sum of the same congruence with itself n times we have 
\[
n  \cdot a \equiv n  \cdot b \Mod{m} 
\]
and so we can multiply either side by $n \in \mathbb{N} $ 
    \item if $a \equiv b \Mod{m} $ then taking multiplying the congruence by itself $n$ times gives 
        \[
        a^{n}  \equiv b^{n}  \Mod{m} 
        \]
        and so we can raise either side of a congruence to any power $n \in \mathbb{N} $. 
\end{itemize}


% section manipulating_congruences (end)
\section{Applications}%
\label{sec:applications}
% section applications

\paragraph{Is $x = 3,974,279$ divisible by $3$? } 
\begin{itemize}
    \item Recall that if the sum of it's digits are divisible by 3, then the whole number is divisible by 3. and the sum of the digits is not divisible by 3, and so $3 \nmid x$ 
        \begin{itemize}
            \item In addition we know $10 \equiv 1 \Mod{3} \because 99\ldots 99  + 1$ 
            \item And since we can raise any congruence to any power we have 
                \[
                10^{n}  \equiv 1 \Mod{3} 
                \]
        \end{itemize}
    \item also recall that $x = 9  \cdot 10^{0}  + \ldots  + 3\left( 10^{6}  \right) $ and so 
        \begin{align*}
            x &\equiv 9\left( 10^{0}  \right)  + \ldots  + 3\left( 10^{6}  \right)  \Mod{3} \\
            &\equiv  9\left( 1 \right)  + \ldots  + 3\left( 1 \right)    \\ 
            &\equiv  \sum \text{ digits  } \\
            &\equiv 41   \\ 
            &\equiv 5   \\ 
            &\equiv 2  
        \end{align*}
\end{itemize}

\paragraph{$2^{29}  + 3$ divisible by 7?} 
\begin{itemize}
    \item observe $29 = 27 + 2 = 3  \cdot 9  + 2$ 
    \item Also $2^{3}  \equiv 8 \equiv 1 \Mod{7} $ and rasing each side of $2^{3}  \equiv 1 \Mod{7} $ to the 9 yields 
        \[
            \left( 2^{3}  \right) 9 \equiv 1^{9}  \Mod{7} \Leftrightarrow 2^{27}  \equiv 1 \Mod{7} 
        \]
        then multiplying both sides by $2^{2} $ we get
        \[
        2^{29}  \equiv 4 \Mod{7} 
        \]
        and adding $3$ to both sides yields 
        \[
            2^{29}  + 3 \equiv 7 \equiv 0 \Mod{7} 
        \]
        thus by definition $7 \mid 2^{29}  + 3  - 0$ so yes!
\end{itemize}

% section applications (end)

% chapter lecture_5 (end)

\end{document}
